In-Rank mesh optimization for URL customized promotion in SEO

### 2015-03-04 MY_PAPERS/article_sduprey_iswag_02_06_2014.tex
iswag

 We here propose an algorithm to automatically compute the optimal internal mesh for our web site. The idea
 behind being simple : the higher you value your URL (potential return on investment), the more in rank you want to give it.

@@

We here choose genetic algorithms among others following here \cite{gen_algo_web}. Simulated annealing, global search, multistart, particle swarm have been tested and also works on the small case to be presented.
But of course, for a real world e-commerce example, those algorithms must not be trusted : they might get stuck into local minima. 
And as we use parameters and randomness for our algorithm, the returned solution might change from one try to another. 
Parameters have to be properly tweaked to proceed through our universe avoiding getting stuck into local minima.

@@

Either we implement it from scratch over a cluster, our algorithm dealing ourselves with concurrency and inter-processor communications,
or we try not to reinvent the wheel and plug ourselves to existing big data platform. We'll here detail our technological choices.

@@

very data we want to optimize our web site from.

@@

the following vector of importance :

@@

Notice that the importance metrics we attribute mirrors the labels we gave. We hope to find back the natural arborescent structure from our algorithm.

@@

We then iterate to find the fixed point solutions of the well know equation :

@@

The fitness function for a mesh $\left(X_i\right)$ is defined as the sum over all nodes of the product of the local importance metrics
and the computed in rank : $\sum^{N}_{i=1} f\left(X_i\right)\times PR(X_i)$, the idea being that by weighing the local importance metrics with the in rank
we'll find the best mesh matching in-rank and the local importance metrics and this for all nodes as the objective is the whole sum. 

@@

Of course, the methodology presented above is still valid. You here just have to change the importance vector you want to

@@

@@

@@

Neo4j is then notified that a property update list is available from Apache Spark on HDFS. Neo4j batch imports the results and applies the updates back to the original graph.

@@

to push forward pages accordingly to an importance metrics. This importance metrics is yours to define. The difficulty here does not lie in the

@@

is here highlighted. It allows a fast ramp-up for anyone to a high level technological state without reinventing the wheel.

>>>>

  We here propose an algorithm to automatically compute the optimal internal mesh for your web site. The idea
  behind being simple : the higher you value your URL, the more in rank you want to give it.

@@

  We here choose genetic algorithms among others following here \cite{gen_algo_web}. 
  But of course, as heuristic, this algorithm must not be trusted : it might get stuck into local minima, depend upon initial set-up and randomness stream seed. 
  Parameters also have to be properly tweaked to proceed through our universe avoiding getting stuck into local minima.
  Other metaheuristics such as global search, multistart, particle swarm or simulated annealing as in \cite{sim_annealing} 
  are also being tested. All seem promising. Robustness toward a general minimum, convergence fastness should here give the prevailing algorithm and its appropriate parameters. 

@@

  Either we implement it from scratch over a cluster dealing ourselves with concurrency and inter-processor communications,
  or we try not to reinvent the wheel and plug ourselves to existing big data cluster platform. We'll here detail our technological choices.

@@

  very data we want to optimize our web site from. $\left(f\left(X_i\right)\right)$ will also be named 'prominence vector' as
  it carries the specific metrics we want to optimize our mesh against.

@@

  the following prominence vector :

@@

  Notice that the prominence metrics vector we attribute mirrors the labels we gave. We hope to find back the natural arborescent structure from our algorithm.

@@

  We then iterate to find the fixed point probability $P$ solution of the well know equation where $c$ is the damping factor set around $0.85$ :

@@

  The fitness function for a mesh $\left(X_i\right)$ is defined as the sum over all nodes of the product of the local prominence metrics
  and the computed in rank : $\sum^{N}_{i=1} f\left(X_i\right)\times PR(X_i)$, the idea being that by weighing the local prominence metrics with the in rank
  we'll find the best mesh matching in-rank and the local prominence metrics and this for all nodes as the objective is the whole sum. 

@@

  Of course, the methodology presented above is still valid. You here just have to change the prominence vector you want to

@@

  The problem here is that the very same restrictions that enable graph-parallel systems as GraphX to achieve substantial performance gains also 
  limit their ability to express many of the important stages in the feeding process of new graph to be computed.
  As Spark GraphX is optimized for iterative diffusion algorithms like PageRank it is not well suited to more basic tasks like constructing the graph,
  modifying its structure, or expressing computation that spans multiple graphs.

@@

  This allows us to pilote the distributed algorithm from a small client (the creation of the graph population and its evolution). Note here that
  the bits vector representation of our mesh is here indeed changed to a sparse adjacency matrix for the page rank computation.

@@

  Neo4j is then notified that a property update list is available from Apache Spark on HDFS. Neo4j batch imports the results and applies the updates back to the original graph,
  where the fitness function can now be computed for the individual.

@@

  to push forward pages accordingly to an prominence metrics which is yours to define. The difficulty here does not lie in the

@@

  is here highlighted. It allows a fast ramp-up for anyone to a high level technological state.
